---
title: "Covid19 - Leaflet"
author: "Aman Bhagat"
date: "27/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

## Introduction

In this leaflet demo, I have shown the total number of cases of COVID 19 across globe representing with Circle markers. The size of the Circle markers represents the total number of cases in the Country.

For this I have used Covid 19 dataset till 26/06/2020 to represent the data. 

```{r covid}
##Covid19 Dataset
covid19 <- read.csv("D:/Games/R Workspace/COVID 19/covid19.csv")
head(covid19)

##Countries Coordinates Dataset 
countries <- read.csv("D:/Games/R Workspace/COVID 19/countries.csv")
```

## Data Cleaning and Processing

You can also embed plots, for example:

```{r data cleaning}
## Grouping the data country wise
covid <- covid19 %>% group_by(countriesAndTerritories,geoId) %>% summarize("total.cases" = sum(cases))
covid <- as.data.frame(covid)

##Cleaning the data
covid$countriesAndTerritories <- gsub("_", " ", covid$countriesAndTerritories)
covid$countriesAndTerritories <- gsub("Cases on an international conveyance Japan", "Japan", covid$countriesAndTerritories)
covid$geoId <- gsub("JPG11668" , "JP" , covid$geoId)
covid$geoId <- gsub("UK" , "GB" , covid$geoId)


## Adding Latitude and Longitude values to each location
n <- nrow(covid)

counter <- 1
covid$lon[counter] <- 0
covid$lat[counter] <- 0

while(counter <= n){
  cc <- covid$geoId[counter]
  if(cc %in% countries$country){
    covid$lon[counter] <- countries[grep(cc,countries$country),]$longitude
    covid$lat[counter] <- countries[grep(cc,countries$country),]$latitude
  }
  counter <- counter + 1
}

##Removing the values for which we don't have coordinates
covid<- covid %>% filter(covid$lon != 0)

##Ordering the data with respect to total number of cases in descending order
covid <- covid[(order(-covid$total.cases)),]
cases <- covid$Total.Cases
head(covid)
```

## Cases arround the world

```{r leaflet}
library(leaflet)
leaflet(covid) %>% addTiles() %>% addCircles(weight = 3, radius = covid$total.cases)
```